### 2013-09-14 results.tex
added image:path vol in text

MR and ARFI imaging total prostate volumes were also compared with the weights
and prostate volumes, approximated to be tri-axial ellipsoids, and calculated
from measurements of the prostate semi-principal axes.  That was no significant
correlation between the prostate weight and the image-reconstructed prostate
volumes (Figure~\ref{fig:fig_mr_arfi_weight}, R$^2$ = 0.05 (MR) and 0.13
(ARFI)), and there was XXXX correlation with the ellipsoidal approximation of
the measurement prostate volume and the image-recontructed volumens (Figure
XX).

>>>>

MR and ARFI imaging total prostate volumes were also compared with the weights
and prostate volumes, approximated to be tri-axial ellipsoids, and calculated
from measurements of the prostate semi-principal axes.  That was no significant
correlation between the prostate weight and the image-reconstructed prostate
volumes (Figure~\ref{fig:mr_arfi_weight}(a), R$^2$ = 0.05 (MR) and 0.13
(ARFI)), and there was mild-to-moderate correlation with the ellipsoidal
approximation of the measurement prostate volume and the image-recontructed
volumens (Figure~\ref{fig:mr_arfi_weight}(b), R$^2$ = 0.32 (MR) and 0.71
(ARFI)).
